---
title: 'Justin Trudeau would still win 2019 Canadian Federal Election even if "everyone" had voted'
author: "Wen Wang"
date: "`r format(Sys.time(), '%d %B, %Y')`"
thanks: "Code and data are available at: https://github.com/wangw218/STA304_FinalProject"
abstract: |
  This paper investigated whether Justin Trudeau or Andrew Scheer would win the 2019 Canadian Federal Election if "everyone" had voted by using MRP technique based on GSS and CES datasets. The result is that Justin Trudeau would still win even if everyone had voted. The analysis is important since it might encourage citizens to participate in the election period to choose the governing party they want, especially when there is only a small difference of the win rate of two parties, which might result in a tremendous change in the future of a country.
  
  **keywords**: 2019 Canadian Federal Election, Multilevel Regression Model, Post-Stratification, Logistic Regression Model, everyone voted

output:
  bookdown::pdf_document2:
    toc: false
    number_sections: false
    citation_package: natbib

bibliography: references.bib

--- 

```{r setup, include=FALSE, echo=FALSE}
library(tidyverse)
library(lme4)
library(knitr)
library(pROC)

# Loading in the cleaned survey Data
survey_data <- read_csv("./../outputs/survey_data.csv")

# Loading in the cleaned census Data
census_data <- read_csv("./../outputs/census_data.csv")

```

## 1. Introduction
The voting process is crucial since it would determine the Prime Minister/President of a country. However, this is not true that everyone eligible to vote had voted in the elections and this phenomenon would probably affect the final results. According to an article in The Economist, if "everyone" had voted in 2016 US presidential election, Hillary Clinton would probably be president.[@CiteIntro1]. Based on the information on Statistics Canada, just over three-quarters (77%) of Canadians reported voting in the 2019 federal election [@CiteIntro2], so it could be inferred that Andrew Scheer would probably win the election if "everyone" had voted.

So, how to make "everyone" vote? It is time-consuming and cost-consuming and almost impossible to do a survey among the target population, all Canadians citizens who are above 18 in this case since not everyone would like to participate in the survey. One statistic way to solve this is through multilevel regression and poststratification (MRP). The central idea of MRP is to partition the data into thousands of demographic cells, estimate voter intent at the cell level using a multilevel regression model, and finally aggregate the cell-level estimates in accordance with the target population's demographic composition.[@CiteIntro3]. In this report, I will use MRP to identify whether Andrew Scheer or Justin Trudeau would win the 2019 Canadian federal election if "everyone" had voted.

The proceed is as follows. In the Methodology section (Section 2), two data sets (survey data and cencus data) will be introduced to investigate how MRP could be used to predict whether Andrew Scheer or Justin Trudeau would win the 2019 Canadian federal election if "everyone" had voted. Results of the MRP analysis are provided in the Results section (Section 3), and summary and conclusion of the MPR analysis along with Weaknesses and Next Steps to improve the analysis are presented in Conclusion section (Section 4).



## 2. Methodology

### 2.1 Data
The survey data is from 2019 Canadian Election Study - Online Survey [@citeSurveyData]. This online sample was for Canadian Election Study and was composed of a two-wave panel with a modified rolling-cross section during the campaign period and a post-election recontact wave. We only focus on the campaign period survey (CPS) in this report. The CPS contains an online sample of 37,822 members of the Canadian general population through Qualtrics, with targets stratified by region and balanced on gender and age within each region. The target population is all Canadian citizens or permanent residents who are age 18 or over. The frame population is Canadian citizens or permanent residents who are age 18 or over and saw the survey. The sample population is Canadian citizens or permanent residents who are age 18 or over and filled in the survey.[@citeSurveyDataCodeBook]

The census data is from the General social survey on Family (cycle 31), 2017 [@CensusDataSource]. The GSS program, established in 1985, conducts telephone surveys across the ten provinces. The GSS is recognized for its regular collection of cross-sectional data that allows for trend analysis, and its capacity to test and develop new concepts that address current or emerging issues. For the census data survey, the target population is all people in Canada who are above 15 years old, excluding those from Yukon, Northwest Territories, and Nunavut. Full-time residents of institutions are also excluded. The frame population is people who are above 15 years old and could be contacted by telephones. The sampled population is people who are above 15 years old and took the survey by telephone. Each record in the survey frame was assigned to a stratum within its province. A simple random sample without replacement of records was next performed in each stratum. There are 20,602 respondents and 461 variables in the census data.[@CensusData]

Figure \@ref(fig:surveydata) shows the number of supporters of each party in survey Data. From the plot, we could see the Liberal Party and the Conservative Party have the most number of supporters while the number of supporters of the Liberal Party is slightly larger than the Conservative Party's. There are a lot of people who don't know or prefer not to answer which party they would like to vote and many NA data.

```{r surveydata, fig.cap = "The number of supporters of each Party in survey Data" , echo = FALSE}
survey_data %>%
  ggplot()+
  geom_bar(aes(cps19_votechoice, fill = ..count..),  width = 0.5) +
  labs(caption = "CES Survey Data") +
  theme(axis.text.x = element_text(angle=45, vjust=0.8,hjust = 0.8))+
  scale_fill_gradient(low = "green", high = "red", na.value = NA) +
  xlab("Party") +
  ylab("Count")

```

After comparing and analyzing the survey data and census data, I found age, household income, sex, Province are the common and meaning variables between these two datasets in investing the result of whether Andrew Scheer or Justin Trudeau would win the 2019 Canadian federal election if "everyone" had voted.

I did some data cleaning to match the variables names and values between the two original survey data and census data files. For both of the cleaned census data and survey data, they contain the following variables:

"age_group" with range ("45 to 59","60+", "Age 18 to 29", "Age 30 to 44");
"sex" with range (Female, Male);
"household_income" with range ("\$25,000 to \$49,999",  "\$75,000 to \$99,999", "\$100,000 to \$124,999", \$50,000 to \$74,999", "Less than \$25,000" , "\$125,000 and more");

"province" with range ("Quebec","Manitoba","Ontario","Alberta","Nova Scotia","British Columbia", "Saskatchewan", "Prince Edward Island", "New Brunswick", "Newfoundland and Labrador") for census data and three more territories: Yukon, Northwest Territories and Nunavut, for survey data. The distribution of the province about survey and census data can be found in Appendix A.

In the survey data, there are two more variables, which are called "voteLib"	and "voteCon". Both of them are binary variables, the value 1 indicating the respondent would like to vote for the party. The values of these two variables are gotten based on the value of "cps19_votechoice" variable in the raw census dataset. If the value of cps19_votechoice is "Liberal Party", then "voteLib" is 1, otherwise, it is 0; Similarly, if the value of cps19_votechoice is "Conservative Party", then "voteCon" is 1, otherwise, it is 0.

The overview of our cleaned datasets after removing the NA rows is shown in survey_data Table \@ref(tab:survey) for survey data and Table \@ref(tab:census) for census data.

```{r, echo= FALSE }
survey_data <- na.omit(survey_data)
census_data <- na.omit(census_data)
survey_data <- survey_data %>%
  select(-cps19_votechoice)

```


```{r survey, echo= FALSE }
kable(head(survey_data), caption = "Overview of Survey Data")

```

```{r census,  echo= FALSE}
kable(head(census_data), caption = "Overview of Census Data")

```


The key feature of this study is it has a very large survey data size. After cleaning the useless and NA data, it still has 21513 samples. However, our cleaned census data size is only 20178, which is slightly lower than our survey data size. This means our census data is not that good. This is kind of make sense since our census data was collected in 2017 and our survey data was collected in 2019 and after 2 years, the population size in Canada would increase. The strength of this study is that our survey data has a very large size, which should be very representative to predict the outcome of the 2019 Canadian Federal Election. However, based on the Figure \@ref(fig:surveydata), there are almost 5000 people who don't know or prefer not to say which party he/she would like to vote in the survey. They account for approximately 23% of our cleaned survey data size. In the real election, their choices might be determined and influential, which might result in the inaccuracy of our prediction.


### 2.2 Model

The model I used in this report is MRP as mentioned in the Introduction by running RStudio [@citeRstudio] with R installed [@CiteR]. I use the survey data to fit the multilevel regression model with a binomial family and then apply the fitted model to the cleaned census data by using Post-Stratification.

I will build two similar multilevel regression models, one for the Liberal Party and another for the Conservative Party and apply each model to the census data to get the estimates of the probabilities of voting for the two parties among the 10 provinces in census data. Then I will use the estimated probabilities of voting for the two parties in the 10 provinces to get the estimates of seats in each province for the Liberal Party and the Conservative Party. In this report, I assume the party which got a higher number of seats would become the governing party. In our analysis, the leader of this party would win the 2019 Canadian federal election if "everyone" had voted. More information about the Canada Election rule can be found in [@electionRule]


## Model Specifics

I will introduce the model about the Liberal Party first. I used a logistic regression model as my level 1 model since "voteLib" are binary variables. Since "province" is in Group level based on what we learned in the class, a level 2 model would be built to account for different intercepts for level 1 model when provinces are different. The level 1 and level 2 models about the Liberal Party are shown as Equation \@ref(eq:eq1) and Equation \@ref(eq:eq2) respectively:

\begin{equation} \label{eq:eq1}
  \begin{aligned}
    log(\frac{\hat{P}}{1-\hat{P}}) &= \beta_{0j} + \beta_{1}x_{age\_group60+,j} + \beta_{2}x_{age\_group18-29,j} + \beta_{3}x_{age\_group30-44,j}\\                                     &+ \beta_{4}x_{sexMale,j}  \\
                                & +\beta_{4}x_{household\_income\$125,000+,j} + \beta_{5}x_{household\_income\$25,000-\$49,999,j} \\                                                & +\beta_{6}x_{household\_income\$50,000-\$74,999,j} + \beta_{7}x_{household\_income\$75,000-\$99,999,j}
  \end{aligned}
\end{equation}

\begin{equation} \label{eq:eq2}
  \beta_{0j}=r_{00} + r_{01}W_{j}
\end{equation}



In the level 1 model (Equation \@ref(eq:eq1)), $\hat{P}$ is the dependent variable and represents the probability of voting for the Liberal Party.
There are 3 independent variables, age_group, sex and household_income. Since they are all categorical, dummy variable encoding is used for all of them, resulting in the Equation \@ref(eq:eq1)). j is the j province. $\beta_{0j}$ is the intercept, which is the dependent variable in the level 2 model.

$\beta_{0j}$ shows the log odds of the probability of voting for the Liberal Party when age_group is "45 to 60", Sex is Female and household income is "\$100,000 to \$124,999".

For other $\beta$s, $\beta_1$, $\beta_2$, $\beta_3$, $\beta_4$, they are all slope parameters. Each of them shows the change in log odds of the probability of voting for the Liberal Party when the responding x value changes from 0 to 1. Actually, these x values can only be 0 or 1 since they are dummy variables. More specifically, $x_{age\_group60+,j}$, $x_{age\_group18-29,j}$ and $x_{age\_group30-44,j}$ can only have one variable be 1 at the same time since a person can only in one age group every time or they can be all 0, which indicates the age group is "45 to 60". Same logic applies on the variables about household income.


In the level 2 model (Equation \@ref(eq:eq2)),$\beta_{0j}$ is the predicated intercept of the level 1 model, and each value for j corresponds to a different province. $r_{00}$ is the intercept of the level 2 model. $r_{01}$ is the slope parameter. $W_{j}$ is the independent variable that influencing province.


The multilevel regression model about Conservative Party and the understanding is the same as Liberal Party's, except now in level 1, the dependent variable $\hat{P}$ represents the probability of voting for the Conservative Party.


```{r, echo= FALSE}
model_Lib<- glmer(voteLib~(1|province) + age_group + sex + household_income, data = survey_data, family=binomial)
summary_L = summary(model_Lib)
```

```{r, echo= FALSE}
model_Con <- glmer(voteCon~(1|province) + age_group + sex + household_income, data = survey_data, family=binomial)
summary_C = summary(model_Con)
```



## Post-Stratification

```{r, echo= FALSE}
reduced_data <- census_data

census_data <-
  census_data%>%
  count(sex, province, age_group,household_income) %>%
  group_by(sex, province, age_group,household_income) %>%
  ungroup()

# Make proportions
census_data <-
  census_data %>%
  group_by(province) %>%
  mutate(total = sum(n)) %>%
  mutate(cell_prop_of_division_total = n / total) %>%
  ungroup()
```

In this section, I would do post-stratification: apply the models I built to the census data. Post-Stratification is the practice of partitioning data into thousands of demographic cells, and the final estimation is calculated by the weighted estimate for each cell. This technique could reduce the bias from non-probability based sampling. To begin the post-stratification process, for each province, I partition the data into demographic cells by age_group, sex and household income. This is also the reason why when I do the data cleaning process, I make these variables to be categorical.

To do Post-Stratification on the Liberal Party's model: the post-stratification formula (Equation \@ref(eq:eq5)) would be used to calculate the probability of voting for the Liberal Party for each province:

\begin{equation} \label{eq:eq5}
  \hat{y}^{PS}=\frac{\Sigma N_{j} \hat{y}_{j}}{\Sigma N_{j}}
\end{equation}

In Equation \@ref(eq:eq5), $\hat{y}^{PS}$ is the estimated probability of voting for the Liberal Party in a particular province; $\hat{y}_{j}$ is the estimate of probability of voting for the Liberal Party in each cell of that province; $N_{j}$ is the number of voters of the $j^{th}$ cell for that province.

Post-Stratification on the Conservative Party's model would use a same equation as the Liberal Party's except $\hat{y}^{PS}$ is now the estimated probability of voting for the Conservative Party and  $\hat{y}_{j}$ is the estimate of probability of voting for the Conservative Party in each cell for a particular province.

Using Post-Stratification, we would get the estimated probability of voting for these two parties. To figure out whether Andrew Scheer or Justin Trudeau would win the 2019 Canadian federal election if "everyone" had voted, we need to look at the total number of seats these two parties got. I would estimate the number of seats each party got from a province by the product of the probability of voting for the party in that province and the number of seats that province have. Then the total number of seats each party got is the sum of the seats they got in all provinces. The results would be shown in Result section.


## Model Check

Before moving to the Result Part, I would discuss if the models I chose are good and valid. I will verify this by using the ROC curve technique. If the area under curve (AUC), is greater than 0.5, I could consider my models are good [@AUC].

```{r include=FALSE}
predict_Lib <- predict(model_Lib, type = 'response')
roc <- roc(survey_data$voteLib, predict_Lib)
```

```{r ROCLib, fig.cap= "ROC curve of Liberal Party Model", echo=FALSE, warning= FALSE}
plot(roc, auc.polygon=TRUE, print.auc = TRUE,asp = NA)
```

```{r, include=FALSE}
predict_Con <- predict(model_Con, type = 'response')
roc <- roc(survey_data$voteCon, predict_Con)
```

```{r ROCCon, fig.cap= "ROC curve of Conservative Party Model",echo=FALSE}
plot(roc, auc.polygon=TRUE, print.auc = TRUE,asp = NA)
```

From the Figure \@ref(fig:ROCLib) and Figure \@ref(fig:ROCCon), we could see the AUC for both of them are much greater that 0.5. Therefore, I could conclude my models are good and valid.

More explanation and analysis about the coefficients of the two models could be found in Appendix A.


```{r,echo = FALSE}
#log estimates for liberal party
census_data$log_estimate_L <-
  model_Lib %>%
  predict(newdata = census_data)

#estimates for liberal party
census_data$estimate_L<-
  exp(census_data$log_estimate_L)/(1+exp(census_data$log_estimate_L))

#estimates for liberal party in each province
estimates_L <- census_data %>%
  mutate(alp_predict_prop_L = estimate_L * cell_prop_of_division_total) %>%
  group_by(province) %>%
  summarise(probability = sum(alp_predict_prop_L))

#log estimates for conservative party
census_data$log_estimate_C <-
  model_Con %>%
  predict(newdata = census_data)

#estimates for conservative party
census_data$estimate_C<-
  exp(census_data$log_estimate_C)/(1+exp(census_data$log_estimate_C))

#estimates for conservative party in each province
estimates_C <- census_data %>%
  mutate(alp_predict_prop_C = estimate_C * cell_prop_of_division_total) %>%
  group_by(province) %>%
  summarise(probability = sum(alp_predict_prop_C))
```

## Alternative Model

It should be acceptable by just using a logistic regression model with the 4 variables: province,age_group,sex,household_income all be categorical. However, the drawback of the logistic regression model is that it does not take into account that different provinces might result in different intercepts as seen in level 1 of the multilevel regression model (Equation \@ref(eq:eq1)). A single logistic regression model may not as accurate as the multilevel regression model. However, it would run faster than multilevel regression model, especially when there are a lot of level 2 variables in the multilevel regression model. It would be time-efficient. In our case, the level 2 only contain the "Province" variable, the multilevel regression model running time is not long and it would be logically more accurate than a single logistic regression model, so I chose multilevel regression model as my final model.


## 3. Results

Table \@ref(tab:resultT) shows the Probability of voting for the Liberal Party among each province.

```{r resultT, echo = FALSE}
kable(estimates_L, caption = "Probability of voting the Liberal Party among each province")
```

Table \@ref(tab:resultS) shows the Probability of voting for the Conservative Party among each province.
```{r resultS,echo = FALSE}
kable(estimates_C, caption = "Probability of voting the Conservative Party among each province")
```

Based on Elections Canada [@seats], the number of seats each province/Territory has is as Table \@ref(tab:seatTable)

```{r seatTable, echo = FALSE}
Seats = c(34,42,14,19,7,11,121,4,78,14)
terriotoris  = c ("Yukon",	"Northwest Territories", "Nunavut")
provinces = c(estimates_L$province, terriotoris)
total_seats = c(Seats, c(1,1,1))
seats_table = data.frame("Province/Territory" = provinces , "TotalSeats" =  total_seats)
kable(seats_table, col.names = gsub("[.]", " ", c("Province/Territory", "Total Seats")),  caption = "Allocation of Seats in the House of Commons" )
```

Notice in our census data, the three territories are excluded, therefore the number of seats each party got is estimated only by the 10 provinces.

The total number of seats each party got is shown in Figure \@ref(fig:seatsResult):

```{r seatsResult, echo = FALSE, fig.cap = "Number of Seats of Liberal Party and Conservative Party"}

Lib_Seats <- round(sum(estimates_L$probability * Seats), digits = 0)
Con_Seats <- round(sum(estimates_C$probability * Seats), digits = 0)

Party = c("Liberal Party Seats","Conservative Party Seats")
Count = c(Lib_Seats,Con_Seats)
result_table = data.frame(Party,Count)

ggplot(data=result_table, aes(x=Party, y=Count)) +
   geom_bar(stat="identity", fill=c("red","steelblue"), width=0.5)+
  geom_text(aes(label=Count), vjust=-0.3, size=3)

```

According to Figure \@ref(fig:seatsResult), the estimated result is that the number of seats the Liberal Party got would be 104 and the number of seats the Conservative Party got would be 97. This is based off the number of seats in each province and and the post-stratification analysis of the proportion of voters in each province in favour of the Liberal Party and the Conservative Party modeled by two multilevel regression models with a binomial family, where the level 1 logistic model accounted for sex, age_group, household_income and level 2 model accounted for province.

It is clear Justin Trudeau would still win the 2019 Canadian federal election even if "everyone" had voted since the Liberal Party has 7 more seats than the Conservative Party. The result still would not change even if we assume the Conservative Party won the 3 seats in Yukon, Northwest Territories and Nunavut.

## 4. Discussion

In the paper, I investigated if the 2019 Canadian federal election result would change if "everyone" had voted, specifically, if Andrew Scheer would win the election instead of Justin Trudeau, by using MRP technique. I chose the 2019 Canadian Election Study - Online Survey as my survey data and the General social survey on Family (cycle 31), 2017 as my census data. First, I cleaned the data in order to do further analysis. I chose four common and meaningful variables between the survey and census data: sex, household income, age, province to do the analysis. In order to do post-stratification, I classified the continuous variables, household income and age, to be categorical with the same range. In addition, I made two new binary variables, voteLib and voteCon, based on the variable "cps19_votechoice" with the question being "Which party do you think you will vote for?" in Survey data. "voteLib" stands for "voting for Liberal Party" and value 1 means the respondent would like to vote for it and 0 means not. voteCon has the same logic but it's for the Conservative Party. The overview of the cleaned survey and census data can be found in Table \@ref(tab:survey)and Table \@ref(tab:census). The cleaned survey data has 21513 samples while cleaned census data size is only 20178. Obviously, this is a drawback.

After the data were cleaned, I built two multilevel Regression models using a binomial family based on the survey data to predict the probability of voting for the Liberal Party and the Conservative Party. Then I use these two models to do post-stratification based on province in census data, splitting cells based on sex, household income and age group. After Post-Stratification, we would get the estimated probability of voting for these two parties among the 10 provinces, as shown on Table \@ref(tab:resultT) and Table \@ref(tab:resultS). Then I estimated the number of seats each party got from every province by the product of the probability of voting for the party in that province and the number of seats that province have according to the data on Table \@ref(tab:seatTable). Then the total number of seats each party got is the sum of the seats they got in all provinces. Finally, I got the result that Liberal Party would get 104 seats and Conservative Party would get 97 seats (Figure \@ref(fig:seatsResult)), so Justin Trudeau would still win the 2019 Canadian federal election even if "everyone" had voted.

In our analysis, Justin Trudeau would still win the 2019 Canadian federal election even if "everyone" had voted but the Liberal Party only have 7 more seats than Conservative Party. However, in other cases, the governing party might change and this might have a great influence on the country and the world. Like the example in the Introduction section, if "everyone" had voted in 2016 US presidential election, Hillary Clinton would probably be president [@CiteIntro1] and the situation about COVID-19 in America might not be such terrible [@citeHCW], 17,515,091 confirmed cases with 313,748 deaths up to 21st December, 2020 according to World Health Organization [@citeWHO]. This report would encourage every eligible citizen in each country to vote during the election period.

### 4.2 Weaknesses

Generally, there are four weaknesses in our model and prediction.

First, the cleaned survey dataset has 21513 samples while the cleaned census data size is only 20178, which means the cleaned census data size is too small. In addition, the census data was collected in 2017 [@CensusDataSource], which would have differences with the population size in 2019 and would increase the bias.

Second, there are almost 5000 people (Figure \@ref(fig:surveydata)) who don't know or prefer not to say which party he/she would like to vote in the survey data, which account for approximately 23% of the cleaned survey data size. In the real election, their choices might be determined and influential, which might result in the inaccuracy of our prediction. 

Third, the census data excludes people from Yukon, Northwest Territories, and Nunavut. When we do post-stratification on the census data, we could not get the estimates of the probabilities of voting for the Liberal Party and the Conservative Party among these three territories, which would result in the lower estimates of total seats each party got, although these three territories only have 3 seats and would not change our final prediction result in this case since the Liberal Party have 7 more seats than Conservative Party.

Lastly, our models only use 4 variables: sex, age group, household income and province. This is not a large number of explanatory variables. If more variables like education and race could be used in our models, the prediction result would be more accurate and less biased.

### 4.3 Next Steps
There are 3 next steps we could do to improve our analysis.

First, find a greater census dataset that was collected in 2019 and contains all regions of Canada to do the Post-Stratification to increase the accuracy of the prediction. 

Second, include more explanatory variables in our models to make the models better.

Third, try learn deeper knowledge about statistics and see if can build more proper models.


## Appendix A

Figure \@ref(fig:surveyP) and Figure \@ref(fig:censusP) show the total observations of different provinces in raw survey Data and census data respectively, where we could see in the survey data there are three more territories: Yukon, Northwest Territories and Nunavut and the respondents in these three territories are much less than those in the other 10 provinces.

```{r surveyP, fig.cap = "Total observations of different provinces in survey Data" , echo = FALSE}
survey_data %>%
  ggplot()+
  geom_bar(aes(province, fill = ..count..),  width = 0.5) +
  labs(caption = "CES Survey Data") +
  theme(axis.text.x = element_text(angle=30, vjust=0.8,hjust = 0.8))+
  scale_fill_gradient(low = "green", high = "red", na.value = NA) +
  xlab("Province") +
  ylab("Count")

```


```{r censusP,fig.cap = "Total observations of different provinces in census Data", echo= FALSE}
reduced_data %>%
  ggplot()+
  geom_bar(aes(province, fill = ..count..),  width = 0.5) +
  labs(caption = "GSS Census Data") +
  theme(axis.text.x = element_text(angle=30, vjust=0.8,hjust = 0.8))+
  scale_fill_gradient(low = "green", high = "red", na.value = NA) +
  xlab("Province") +
  ylab("Count")
```

## Appendix B

From the Table \@ref(tab:Ttable), most variables about household_income are significant since their p values are small. SexMale is not significant since it has a large p value but the intercept has a very small p value, we could infer SexFemale should be significant. In addition, we could infer and conclude age_group from 45 to 59 should be significant. Overall, most variables are significant. This multilevel regression model is a good model for predicating the probability of voting for the Liberal Party.

From the Table \@ref(tab:Stable), most variables about age_group, sex and household_income are significant since their p values are small except "household_income\$50,000 to \$74,999" and 
"household_income\$75,000 to \$99,999". This multilevel regression model is a good model for predicating the probability of voting for the Conservative Party.

```{r Ttable, echo = FALSE}
kable(summary_L$coefficients, caption = "Summary of Cofficient of the Liberal Party model")
```

```{r Stable, echo = FALSE}
kable(summary_C$coefficients, caption = "Summary of Cofficient of the Conservative Party model")
```


## Appendix C
In this report, we used R [@CiteR], Rstudio [@citeRstudio] and R packages: tidyverse [@package1],lme4 [@package2], knitr [@kable1] [@kable2] [@kable3], cesR [@cesR], labelled [@labelled] and pROC [@citeROC].
















